Structural Divergence Analysis

### 2016-12-11 analysis-structure3-core.Rmd
cambios 11/12/16

```{r set_file_names}
# set input filenames
## data
reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))
site.info.fname = file.path(data.dir, paste(p.ref, "_m.da.ca.csv", sep = ""))
min.da.CM.CA.fname = file.path(data.dir, paste(p.ref, "_min.da.CM.ca.csv", sep = ""))

@@

@@

# add pdb.info to site.info
site.info = cbind(site.info, pdb.info)
```

```{r read_data}
# read data
## exp
dri2.exp = read.csv(dri2.exp.fname, header = T)
site = site.info$site
dri2.exp = dri2.exp[1:length(protein.exp), site]
rownames(dri2.exp) = protein.exp

## mut
dri2.mut = read.csv(dri2.mut.fname, header = T)
site = site.info$site
dri2.mut = dri2.mut[1:length(protein.exp), site]
rownames(dri2.mut) = paste("mut", rownames(dri2.mut), sep = "")

## strong
dri2.strong = read.csv(dri2.strong.fname, header = T)
site = site.info$site
dri2.strong = dri2.strong[1:length(protein.exp), site]
rownames(dri2.strong) = paste("strong", rownames(dri2.strong), sep = "")
```

@@

r.exp.mut = cor(d.exp$mean.z.RSD, d.mut$mean.z.RSD)
r.exp.strong = cor(d.exp$mean.z.RSD, d.strong$mean.z.RSD)
r.mut.strong = cor(d.mut$mean.z.RSD, d.strong$mean.z.RSD)

@@

# comparison of means.z.scores with the minimum distance to the functional sites
plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.ca, xlab = "minimal distance to active site (between CAs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.CM, xlab = "minimal distance to active site (between CMs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")

## calculate correlations between profiles
r.min.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.ca)
r.min.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.CM)

cor.df = data.frame("comparison" = c("(exp - mut) vs min.da.CA", "(exp - mut) vs min.da.CM"), "R" = c(r.min.da.CA, r.min.da.CM))

knitr::kable(cor.df, digits = 2, caption = "Correlation between differences in <Z-scores> profiles and the minimal distance to the active site")
```

>>>>

```{r set_file_names}
# set input filenames
## data
reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))
site.info.fname = file.path(data.dir, paste(p.ref, "_m.da.ca.csv", sep = ""))
min.da.CM.CA.fname = file.path(data.dir, paste(p.ref, "_m.da.ca.csv", sep = ""))

@@

```{r read_the_core, comment = ""}
# indexes.core
indexes.core = as.numeric(read.csv(file.path("DATA", paste("indexes.core.2", "_", family, ".csv", sep = "")))[1, -1])
```

@@

# add pdb.info to site.info
site.info = cbind(site.info[indexes.core, ], pdb.info[indexes.core, ])
```

```{r read_data}
# read data
## exp
dri2.exp = read.csv(dri2.exp.fname, header = T)[, indexes.core]
rownames(dri2.exp) = protein.exp

## mut
dri2.mut = read.csv(dri2.mut.fname, header = T)[, indexes.core]
rownames(dri2.mut) = paste("mut", rownames(dri2.mut), sep = "")

## strong
dri2.strong = read.csv(dri2.strong.fname, header = T)[, indexes.core]
rownames(dri2.strong) = paste("strong", rownames(dri2.strong), sep = "")
```

@@

# calculate cors
r.exp.mut = cor(d.exp$mean.z.RSD, d.mut$mean.z.RSD)
r.exp.strong = cor(d.exp$mean.z.RSD, d.strong$mean.z.RSD)
r.mut.strong = cor(d.mut$mean.z.RSD, d.strong$mean.z.RSD)

@@

```

```{r_comparison_vs_plots}

# plot exp vs simulated profiles 
par(pty = "s")

plot(x = d.exp$mean.z.RSD, 
     y = d.mut$mean.z.RSD, 
     xlab = "exp.mean.z.RSD", 
     ylab = "mut.mean.z.RSD", 
     xlim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))),
     ylim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))))
points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.mut$mean.z.RSD)[active.sites], col = "yellow")
points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], col = "green")
abline(0, 1)

plot(x = d.exp$mean.z.RSD, 
     y = d.strong$mean.z.RSD, 
     xlab = "exp.mean.z.RSD", 
     ylab = "strong.mean.z.RSD", 
     xlim = c(min(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD))),
     ylim = c(min(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD))))
points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.strong$mean.z.RSD)[contacts.active.sites], col = "green")
points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.strong$mean.z.RSD)[active.sites], col = "yellow")
abline(0, 1)

plot(x = d.mut$mean.z.RSD, 
     y = d.strong$mean.z.RSD, 
     xlab = "mut.mean.z.RSD", 
     ylab = "strong.mean.z.RSD", 
     xlim = c(min(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD))),
     ylim = c(min(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD))))
points(x = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.strong$mean.z.RSD)[contacts.active.sites], col = "green")
points(x = as.numeric(d.mut$mean.z.RSD)[active.sites], y = as.numeric(d.strong$mean.z.RSD)[active.sites], col = "yellow")
abline(0, 1)
```

### 2016-12-11 analysis-structure3.Rmd
cambios 11/12/16

>>>>

```{r_comparison_vs_plots}

# plot exp vs simulated profiles 
par(pty = "s")

plot(x = d.exp$mean.z.RSD, 
     y = d.mut$mean.z.RSD, 
     xlab = "exp.mean.z.RSD", 
     ylab = "mut.mean.z.RSD", 
     xlim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))),
     ylim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))))
points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.mut$mean.z.RSD)[active.sites], col = "yellow")
points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], col = "green")
abline(0, 1)

plot(x = d.exp$mean.z.RSD, 
     y = d.strong$mean.z.RSD, 
     xlab = "exp.mean.z.RSD", 
     ylab = "strong.mean.z.RSD", 
     xlim = c(min(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD))),
     ylim = c(min(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD))))
points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.strong$mean.z.RSD)[contacts.active.sites], col = "green")
points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.strong$mean.z.RSD)[active.sites], col = "yellow")
abline(0, 1)

plot(x = d.mut$mean.z.RSD, 
     y = d.strong$mean.z.RSD, 
     xlab = "mut.mean.z.RSD", 
     ylab = "strong.mean.z.RSD", 
     xlim = c(min(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD))),
     ylim = c(min(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD))))
points(x = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.strong$mean.z.RSD)[contacts.active.sites], col = "green")
points(x = as.numeric(d.mut$mean.z.RSD)[active.sites], y = as.numeric(d.strong$mean.z.RSD)[active.sites], col = "yellow")
abline(0, 1)
```
